Expression QTL hotspot dissection with mediation analysis and pleiotropy testing

### 2019-07-31 analysis/paper/hotspots-paper.Rmd
set eval to FALSE for code chunk about Tmem189

```{r scan1}
# read oddball points from interactive plot
tr <- c("Tmem189",
        "Myo15b",
        "Sephs2",
        "Bcmo1",
        "Tmprss4",
        "Cacnb3",
        "Gm12929",
        "Eya2"
        )
tr_tib <- hot_annot %>%
  filter(symbol %in% tr) %>%
  arrange(annot.id)
K <- readRDS(here("analysis", "data", "derived_data", "kinship.rds"))
map <- readRDS(here("analysis", "data", "derived_data", "map.rds"))
covar <- readRDS(here("analysis", "data", "derived_data", "covar.rds"))
aprobs <- readRDS(here("analysis", "data", "derived_data", "genoprobs.rds"))
expr_sm <- expr[ , colnames(expr) %in% tr_tib$annot.id, drop = FALSE]
s1 <- qtl2::scan1(genoprobs = aprobs,
            pheno = expr_sm,
            kinship = K,
            addcovar = covar, 
            cores = 0
)
# zoom in on Chr2 after 150 Mb
# get length of map$`1`
purrr::map(.x = 1:8, .f = function(x) qtl2::plot_scan1(s1, map, lodcolumn = x, chr = 2, main = paste0(tr_tib[x, ])))
qtl2::find_peaks(scan1_output = s1, map = map, threshold = 7) %>% 
  as_tibble() %>%
  filter(chr == 2) %>%
  left_join(hot_annot, by = c("lodcolumn" = "annot.id"))
```

>>>>

```{r scan1-Chr2, eval = FALSE}
# read oddball points from interactive plot
tr <- c("Tmem189",
        "Myo15b",
        "Sephs2",
        "Bcmo1",
        "Tmprss4",
        "Cacnb3",
        "Gm12929",
        "Eya2"
        )
tr_tib <- hot_annot %>%
  filter(symbol %in% tr) %>%
  arrange(annot.id)
K <- readRDS(here("analysis", "data", "derived_data", "kinship.rds"))
map <- readRDS(here("analysis", "data", "derived_data", "map.rds"))
covar <- readRDS(here("analysis", "data", "derived_data", "covar.rds"))
aprobs <- readRDS(here("analysis", "data", "derived_data", "genoprobs.rds"))
expr_sm <- expr[ , colnames(expr) %in% tr_tib$annot.id, drop = FALSE]
s1 <- qtl2::scan1(genoprobs = aprobs,
            pheno = expr_sm,
            kinship = K,
            addcovar = covar, 
            cores = 0
)
# zoom in on Chr2 after 150 Mb
# get length of map$`1`
purrr::map(.x = 1:8, .f = function(x) qtl2::plot_scan1(s1, map, lodcolumn = x, chr = 2, main = paste0(tr_tib[x, ])))
qtl2::find_peaks(scan1_output = s1, map = map, threshold = 7) %>% 
  as_tibble() %>%
  filter(chr == 2) %>%
  left_join(hot_annot, by = c("lodcolumn" = "annot.id"))
```
